JavaScript as an Embedded DSL

### 2012-03-30 papers/ecoop2012/article.tex
Add ref to section where snowflake is described.

We propose to embed JavaScript as a DSL in a host language.\footnote{Surely, the embedded language is not exactly JavaScript: it naturally is a subset of Scala, the host language. However, it is quite close to JavaScript: often one can take snippets of JavaScript code and use them in the DSL with minor syntactic tweaking (as demonstrated by the Snowflake example).} Through LMS, we tackle the challenges outlined above with minimal effort, as most of the work is off-loaded to the host language. In particular, we make the following contributions:
\begin{itemize}
\item Our DSL is statically typed through the host language, yet supports gradual typing notably for incorporating external JavaScript libraries and APIs (section~\ref{sec:typing}).
\item In addition to generating JavaScript code, our DSL can be executed directly in the host language, allowing code to be shared between client and server (section~\ref{sec:trivial-embedding}).
\item We use advanced object-oriented techniques to achieve modularity in our DSL: each language primitive and API is defined in a separate module (section~\ref{sec:modularity}).
\item Our DSL supports typed object literals and class-based objects. The translations to JavaScript are lightweight and intuitive: the object literals translate to JSON-like object literals and the class-based objects to JavaScript constructor-based objects (section~\ref{sec:reification}).
\item With minimal effort, we exploit the selective CPS transform already existing in the host language to provide a compelling abstraction over asynchronous callback-driven programming in our DSL (section~\ref{sec:cps}). This case-study demonstrates the fruitfulness of re-using host language features to enhance our embedded DSL. A novel insight is that CPS transforming a program generator allows it to generate code that is in CPS.
\end{itemize}

>>>>

We propose to embed JavaScript as a DSL in a host language.\footnote{Surely, the embedded language is not exactly JavaScript: it naturally is a subset of Scala, the host language. However, it is quite close to JavaScript: often one can take snippets of JavaScript code and use them in the DSL with minor syntactic tweaking (as demonstrated by the Snowflake example described in section \ref{sec:trivial-embedding}).} Through LMS, we tackle the challenges outlined above with minimal effort, as most of the work is off-loaded to the host language. In particular, we make the following contributions:
\begin{itemize}
\item Our DSL is statically typed through the host language, yet supports gradual typing notably for incorporating external JavaScript libraries and APIs (section~\ref{sec:typing}).
\item In addition to generating JavaScript code, our DSL can be executed directly in the host language, allowing code to be shared between client and server (section~\ref{sec:trivial-embedding}).
\item We use advanced object-oriented techniques to achieve modularity in our DSL: each language primitive and API is defined in a separate module (section~\ref{sec:modularity}).
\item Our DSL supports typed object literals and class-based objects. The translations to JavaScript are lightweight and intuitive: the object literals translate to JSON-like object literals and the class-based objects to JavaScript constructor-based objects (section~\ref{sec:reification}).
\item With minimal effort, we exploit the selective CPS transform already existing in the host language to provide a compelling abstraction over asynchronous callback-driven programming in our DSL (section~\ref{sec:cps}). This case-study demonstrates the fruitfulness of re-using host language features to enhance our embedded DSL. A novel insight is that CPS transforming a program generator allows it to generate code that is in CPS.
\end{itemize}
